Cognitive and Auditory Predictors of Dysarthric Speech Understanding in Older

### 2024-01-05 Manuscript Analyses/manuscript_analysis.Rmd
Added Initial PD model comparison
Added additional corr matricies

First, pretest and posttest intelligibility was calculated as percent words correct (pwc) for each listener.

@@

A total of 60 older adult listeners participated in the study. The overall demographic information for the participants are below.

@@

@@

# AM1 Cor Plot
AM1_cor <- cor_df %>%
  dplyr::filter(speaker == "AM1") %>%
  dplyr::select(!c(id, speaker, fluid_cog_c, posttest)) %>%
  dplyr::rename(
    `Working Memory` = list_sort_c,
    `Inhibitory Control` = flanker_c,
    `Cognitive Flexibility` = card_sort_c,
    `Receptive Vocabulary` = vocab_c,
    `Processing Speed` = pattern_c,
    `Picture Sequence Memory` = pic_seq_c,
    `Words in Noise Threshold` = best_win
  ) %>%
  dplyr::rename_all(snakecase::to_title_case) %>%
  cor(use = "pairwise.complete.obs") %>%
  ggcorrplot(
    type = "lower",
    outline.col = "white",
    colors = c(my_pal[1], "white", my_pal[15]),
    lab = TRUE,
    sig.level = 0.05,
    insig = "blank",
    title = "Ataxic", 
    legend.title = "Correlation"
  )

@@

@@

@@

@@

>>>>

First, pretest and posttest intelligibility was calculated as a percent words correct (pwc) score for each listener. Pretest PWC and PWC change (posttest-pretest) will be our outcome variables for the analyses.

@@

A total of 60 older adult listeners participated in the study. The overall demographic information for the participants are in the table below.

@@

Words in noise significantly correlated with pretest intelligibility for AM1 at the alpha = 0.05 level. Listeners with higher (i.e. worse) words in noise hearing thresholds tend to have lower pretest intelligibility (i.e. lower initial intelligibility) for AM1.

@@

# AM1 Cor Plot
AM1_cor <- cor_df %>%
  dplyr::filter(speaker == "AM1") %>%
  dplyr::select(!c(id, speaker, fluid_cog_c, posttest)) %>%
  dplyr::rename(
    `Working Memory` = list_sort_c,
    `Inhibitory Control` = flanker_c,
    `Cognitive Flexibility` = card_sort_c,
    `Receptive Vocabulary` = vocab_c,
    `Processing Speed` = pattern_c,
    `Picture Sequence Memory` = pic_seq_c,
    `Words in Noise Threshold` = best_win
  ) %>%
  dplyr::rename_all(snakecase::to_title_case) %>%
  cor(use = "pairwise.complete.obs") %>%
  ggcorrplot(
    type = "lower",
    outline.col = "white",
    colors = c(my_pal[1], "white", my_pal[15]),
    lab = TRUE,
    insig = "blank",
    title = "Ataxic", 
    legend.title = "Correlation"
  )

@@

The plot below shows only the significant correlations in the matrix above for AM1.

cor_df %>%
  dplyr::filter(speaker == "AM1") %>%
  dplyr::select(!c(id, speaker, fluid_cog_c, posttest)) %>%
  dplyr::rename(
    `Working Memory` = list_sort_c,
    `Inhibitory Control` = flanker_c,
    `Cognitive Flexibility` = card_sort_c,
    `Receptive Vocabulary` = vocab_c,
    `Processing Speed` = pattern_c,
    `Picture Sequence Memory` = pic_seq_c,
    `Words in Noise Threshold` = best_win
  ) %>%
  dplyr::rename_all(snakecase::to_title_case) %>%
  cor(use = "pairwise.complete.obs") %>%
  ggcorrplot(
    type = "lower",
    outline.col = "white",
    colors = c(my_pal[1], "white", my_pal[15]),
    lab = TRUE,
    p.mat = cor_pmat(.),
    sig.level = 0.05,
    insig = "blank",
    title = "Ataxic", 
    legend.title = "Correlation"
  )

@@

Like AM1, words in noise hearing threshold significantly correlated with pretest intelligibility. However, listener processing speed has a weak, but significant, correlation with intelligibility improvement. Pretest intelligibility is also has a negative correlation with intelligibility improvement, indicating that listeners in this group who had higher pretest intelligibility tend to have less intelligibility gains at posttest.

@@

The plot below only shows the significant correlations for PDM10.

cor_df %>%
  dplyr::filter(speaker == "PDM10") %>%
  dplyr::select(!c(id, speaker, fluid_cog_c, posttest)) %>%
  dplyr::rename(
    `Working Memory` = list_sort_c,
    `Inhibitory Control` = flanker_c,
    `Cognitive Flexibility` = card_sort_c,
    `Receptive Vocabulary` = vocab_c,
    `Processing Speed` = pattern_c,
    `Picture Sequence Memory` = pic_seq_c,
    `Words in Noise Threshold` = best_win
  ) %>%
  dplyr::rename_all(snakecase::to_title_case) %>%
  cor(use = "pairwise.complete.obs") %>%
  ggcorrplot(
    type = "lower",
    outline.col = "white",
    colors = c(my_pal[1], "white", my_pal[15]),
    lab = TRUE,
    p.mat = cor_pmat(.),
    insig = "blank",
    sig.level = 0.05,
    title = "Parkinson's Disease", 
    legend.title = "Correlation"
  )

```{r, eval = F, warning = F, message = F}

@@

```{r}
t_for_diff(mods2)
```
